---
title: "06b — Treatment Panels: Antisemitism Outcome (Multi-Figure)"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = TRUE, warning = TRUE)
knitr::opts_knit$set(root.dir = "C:/Users/ammonsj/Ideas")
source("C:/Users/ammonsj/Ideas/_config.R")
source("C:/Users/ammonsj/Ideas/R/build_antisem_panels.R")
```

## Build antisemitism treatment panels

Panels are built by `R/build_antisem_panels.R`, which streams the RoBERTa-scored
corpus **one year at a time**: each year's text file is read once and every
political figure is flagged in that single pass, then the year's articles are
aggregated to the newspaper × month level and only the small monthly aggregates
are accumulated. This keeps peak memory at roughly one year of data (~7–8 GB)
instead of materialising the full ~63 GB scored table — the previous inline
version loaded everything and `clusterExport()`-ed it to 5 workers, which
exceeded the machine's 128 GB and reliably OOM-crashed.

The panel schema is unchanged, so steps 07c and 08b consume these files exactly
as before. Building is resumable: any `did_panel_antisem_<figure>.parquet` that
already exists is skipped (delete it to force a rebuild).

```{r build-panels}
roberta_dir <- ROBERTA_SCORED_DIR
text_dir    <- file.path(DATA_PARQUET, "articles_antisem_scored")

if (length(list.files(roberta_dir, pattern = "\\.parquet$")) == 0) {
  stop("No RoBERTa-scored files found in ", roberta_dir, ". Run step 05c first.")
}

build_all_antisem_panels(
  roberta_dir = roberta_dir,
  text_dir    = text_dir,
  figures     = FIGURES,
  out_dir     = DATA_PANELS
)
```

## Panel summary

```{r summary}
library(arrow)
library(data.table)

panel_files <- list.files(DATA_PANELS, pattern = "^did_panel_antisem_.*\\.parquet$",
                          full.names = TRUE)
message("Antisemitism panel files found: ", length(panel_files))

for (pf in panel_files) {
  fig_key <- gsub(".*did_panel_antisem_(.*)\\.parquet", "\\1", pf)
  fig_name <- if (fig_key %in% names(FIGURES)) FIGURES[[fig_key]]$name else fig_key
  p <- as.data.table(read_parquet(pf))

  p[, ever_treated := as.integer(!is.na(treat_date))]

  summary_by_group <- p[, .(
    `N newspaper-months` = .N,
    `N newspapers` = uniqueN(newspaper_name),
    `Mean antisemitism (RoBERTa)` = round(mean(antisem_rate_roberta, na.rm = TRUE), 4),
    `Mean antisemitism (lexicon)` = round(mean(antisem_rate_lexicon, na.rm = TRUE), 3),
    `Mean figure count` = round(mean(figure_count), 2)
  ), by = .(Group = fifelse(ever_treated == 1, "Treated", "Never Treated"))]

  cat("\n--- ", fig_name, " ---\n")
  print(summary_by_group)

  rm(p)
  gc()
}
```
