---
title: "08 — Publication Figures and Tables (Multi-Figure)"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = TRUE, warning = TRUE,
                      fig.width = 8, fig.height = 6, dpi = 300)
knitr::opts_knit$set(root.dir = "C:/Users/ammonsj/Ideas")
source("C:/Users/ammonsj/Ideas/_config.R")
```

```{r libraries}
library(data.table)
library(arrow)
library(ggplot2)
library(patchwork)
library(fect)
library(usmap)
library(knitr)
```

## Helper functions

```{r helpers}
# Extract ATT from fect models (bootstrap SE)
extract_fect_att <- function(model) {
  att <- as.numeric(model$att.avg)
  se  <- sd(model$att.avg.boot)
  list(att = att, se = se,
       ci_lo = att - 1.96 * se, ci_hi = att + 1.96 * se,
       p = 2 * pnorm(-abs(att / se)))
}

# Extract ATT from did_wrapper models
extract_did_att <- function(model) {
  avg <- model$est.avg
  list(att = avg$ATT.avg, se = avg$S.E.,
       ci_lo = avg$CI.lower, ci_hi = avg$CI.upper,
       p = avg$p.value)
}

# Format a coefficient cell: "coef\n(se)"
fmt_coef <- function(att, se) {
  if (is.na(att)) return("")
  paste0(sprintf("%.4f", att), "\n(", sprintf("%.4f", se), ")")
}

# Format CI
fmt_ci <- function(lo, hi) {
  if (is.na(lo)) return("")
  paste0("[", sprintf("%.4f", lo), ", ", sprintf("%.4f", hi), "]")
}

# Format p-value
fmt_p <- function(p) {
  if (is.na(p)) return("")
  if (p < 0.001) return("$<$0.001")
  sprintf("%.3f", p)
}

# Load newspaper-to-state mapping for maps
np_states <- fread(file.path(DATA_PANELS, "newspaper_states.csv"), encoding = "UTF-8")
np_states <- np_states[state != ""]
message("Loaded ", nrow(np_states), " newspaper-state mappings.")
```

## Per-figure horizontal results tables

```{r horizontal-tables}
fect_methods <- c("ife", "mc", "fe")
fect_labels  <- c(ife = "IFE", mc = "MC", fe = "TWFE (Imp.)")
did_methods  <- c("cs_notyet", "iw", "didm", "twfe")
did_labels   <- c(cs_notyet = "C\\&S", iw = "S\\&A",
                  didm = "dCDH", twfe = "Dyn. TWFE")

all_methods <- c(fect_methods, did_methods)
all_labels  <- c(fect_labels, did_labels)

# Store ATTs for cross-figure forest plot
forest_data <- list()

for (fig_key in names(FIGURES)) {
  fig <- FIGURES[[fig_key]]
  message("\n", strrep("=", 60))
  message("Building table for: ", fig$name, " (", fig_key, ")")
  message(strrep("=", 60))

  # Collect estimates for each method
  att_vals  <- se_vals <- ci_lo_vals <- ci_hi_vals <- p_vals <- rep(NA_real_, length(all_methods))
  names(att_vals) <- names(se_vals) <- names(ci_lo_vals) <- names(ci_hi_vals) <- names(p_vals) <- all_methods

  # --- fect models ---
  for (method in fect_methods) {
    model_path <- file.path(MODELS_DIR, paste0("fect_", method, "_", fig_key, ".rds"))
    if (file.exists(model_path)) {
      m <- readRDS(model_path)
      res <- extract_fect_att(m)
      att_vals[method]  <- res$att
      se_vals[method]   <- res$se
      ci_lo_vals[method] <- res$ci_lo
      ci_hi_vals[method] <- res$ci_hi
      p_vals[method]    <- res$p
      rm(m); gc()
    }
  }

  # --- did_wrapper models ---
  for (method in did_methods) {
    model_path <- file.path(MODELS_DIR, paste0("did_", method, "_", fig_key, ".rds"))
    if (file.exists(model_path)) {
      m <- readRDS(model_path)
      res <- extract_did_att(m)
      att_vals[method]  <- res$att
      se_vals[method]   <- res$se
      ci_lo_vals[method] <- res$ci_lo
      ci_hi_vals[method] <- res$ci_hi
      p_vals[method]    <- res$p
      rm(m); gc()
    }
  }

  # Check if any models were found
  if (all(is.na(att_vals))) {
    message("  No models found for ", fig$name, ", skipping table.")
    next
  }

  # Store IFE result for forest plot
  if (!is.na(att_vals["ife"])) {
    forest_data[[fig_key]] <- data.table(
      figure = fig$name,
      att    = att_vals["ife"],
      se     = se_vals["ife"],
      ci_lo  = ci_lo_vals["ife"],
      ci_hi  = ci_hi_vals["ife"]
    )
  }

  # --- Build horizontal LaTeX table ---
  # Columns: one per method. Rows: ATT/(SE), 95% CI, p-value
  ncols <- sum(!is.na(att_vals))
  active_methods <- all_methods[!is.na(att_vals)]
  active_labels  <- all_labels[active_methods]

  # Build LaTeX manually for precise control
  col_spec <- paste(rep("c", length(active_methods)), collapse = "")

  tex_lines <- c(
    "\\begin{table}[htbp]",
    paste0("\\caption{ATT Estimates: ", fig$name, "\\label{tab:", fig_key, "-results}}"),
    "\\centering",
    "\\small",
    paste0("\\begin{tabular}{l", col_spec, "}"),
    "\\toprule",
    paste0(" & ", paste(active_labels, collapse = " & "), " \\\\"),
    "\\midrule"
  )

  # Row 1: ATT with SE in parentheses below
  att_cells <- sapply(active_methods, function(m) {
    sprintf("%.4f", att_vals[m])
  })
  tex_lines <- c(tex_lines,
    paste0("ATT & ", paste(att_cells, collapse = " & "), " \\\\")
  )

  # Row 2: (SE) — indented, smaller
  se_cells <- sapply(active_methods, function(m) {
    paste0("(", sprintf("%.4f", se_vals[m]), ")")
  })
  tex_lines <- c(tex_lines,
    paste0(" & ", paste(se_cells, collapse = " & "), " \\\\")
  )

  # Row 3: 95% CI
  ci_cells <- sapply(active_methods, function(m) {
    paste0("[", sprintf("%.4f", ci_lo_vals[m]), ", ", sprintf("%.4f", ci_hi_vals[m]), "]")
  })
  tex_lines <- c(tex_lines,
    paste0("95\\% CI & ", paste(ci_cells, collapse = " & "), " \\\\")
  )

  # Row 4: p-value
  p_cells <- sapply(active_methods, function(m) {
    if (p_vals[m] < 0.001) "$<$0.001" else sprintf("%.3f", p_vals[m])
  })
  tex_lines <- c(tex_lines,
    paste0("$p$-value & ", paste(p_cells, collapse = " & "), " \\\\")
  )

  tex_lines <- c(tex_lines,
    "\\bottomrule",
    "\\end{tabular}",
    paste0("\\\\[2pt]"),
    paste0("\\footnotesize\\textit{Note:} Standard errors in parentheses. ",
           "IFE = Interactive Fixed Effects; MC = Matrix Completion; ",
           "TWFE (Imp.) = Two-Way FE (Imputation); ",
           "C\\&S = Callaway \\& Sant'Anna; S\\&A = Sun \\& Abraham; ",
           "dCDH = de Chaisemartin \\& D'Haultfoeuille; Dyn.\\ TWFE = Dynamic TWFE. ",
           "Study window: ", fig$study_start, "--", fig$study_end, "."),
    "\\end{table}"
  )

  tex_string <- paste(tex_lines, collapse = "\n")
  save_table(tex_string, paste0("table_", fig_key, "_results"))
  message("  Saved: table_", fig_key, "_results.tex")

  # Print to console
  cat(tex_string, "\n\n")
}
```

## Per-figure IFE event study plots

```{r ife-event-studies}
for (fig_key in names(FIGURES)) {
  fig <- FIGURES[[fig_key]]
  model_path <- file.path(MODELS_DIR, paste0("fect_ife_", fig_key, ".rds"))

  if (!file.exists(model_path)) {
    message("No IFE model for ", fig$name, ", skipping plot.")
    next
  }

  message("Generating IFE event study for: ", fig$name)

  out_ife <- readRDS(model_path)

  # Use fect's built-in plot (base R)
  pdf(file.path(FIGURES_DIR, paste0("fig_ife_att_", fig_key, ".pdf")),
      width = 8, height = 6)
  plot(out_ife, main = paste0("ATT: ", fig$name, " (IFE)"),
       ylab = "ATT (Incivility Rate)", xlab = "Periods Since Treatment",
       cex.main = 1.2, cex.lab = 1.1)
  dev.off()

  png(file.path(FIGURES_DIR, paste0("fig_ife_att_", fig_key, ".png")),
      width = 8, height = 6, units = "in", res = 300)
  plot(out_ife, main = paste0("ATT: ", fig$name, " (IFE)"),
       ylab = "ATT (Incivility Rate)", xlab = "Periods Since Treatment",
       cex.main = 1.2, cex.lab = 1.1)
  dev.off()

  # Copy to Overleaf
  for (ext in c("pdf", "png")) {
    file.copy(file.path(FIGURES_DIR, paste0("fig_ife_att_", fig_key, ".", ext)),
              file.path(OVERLEAF_FIGURES, paste0("fig_ife_att_", fig_key, ".", ext)),
              overwrite = TRUE)
  }

  rm(out_ife); gc()
  message("  Saved: fig_ife_att_", fig_key)
}
```

## Per-figure placebo test plots

```{r placebo-plots}
for (fig_key in names(FIGURES)) {
  fig <- FIGURES[[fig_key]]
  placebo_path <- file.path(MODELS_DIR, paste0("fect_placebo_", fig_key, ".rds"))

  if (!file.exists(placebo_path)) {
    message("No placebo model for ", fig$name, ", skipping.")
    next
  }

  message("Generating placebo plot for: ", fig$name)

  out_placebo <- readRDS(placebo_path)

  pdf(file.path(FIGURES_DIR, paste0("fig_placebo_", fig_key, ".pdf")),
      width = 8, height = 6)
  plot(out_placebo, main = paste0("Placebo Test: ", fig$name),
       ylab = "ATT (Incivility Rate)", xlab = "Periods Since Treatment",
       cex.main = 1.2, cex.lab = 1.1)
  dev.off()

  png(file.path(FIGURES_DIR, paste0("fig_placebo_", fig_key, ".png")),
      width = 8, height = 6, units = "in", res = 300)
  plot(out_placebo, main = paste0("Placebo Test: ", fig$name),
       ylab = "ATT (Incivility Rate)", xlab = "Periods Since Treatment",
       cex.main = 1.2, cex.lab = 1.1)
  dev.off()

  for (ext in c("pdf", "png")) {
    file.copy(file.path(FIGURES_DIR, paste0("fig_placebo_", fig_key, ".", ext)),
              file.path(OVERLEAF_FIGURES, paste0("fig_placebo_", fig_key, ".", ext)),
              overwrite = TRUE)
  }

  rm(out_placebo); gc()
  message("  Saved: fig_placebo_", fig_key)
}
```

## Per-figure C&S event study plots

```{r cs-event-studies}
for (fig_key in names(FIGURES)) {
  fig <- FIGURES[[fig_key]]
  cs_path <- file.path(MODELS_DIR, paste0("did_cs_notyet_", fig_key, ".rds"))

  if (!file.exists(cs_path)) {
    message("No C&S model for ", fig$name, ", skipping.")
    next
  }

  message("Generating C&S event study for: ", fig$name)

  res_cs <- readRDS(cs_path)
  cs_att <- tryCatch({
    dt <- as.data.table(res_cs$est.att)
    dt[, period := as.integer(rownames(res_cs$est.att))]
    dt[period >= -24 & period <= 24]
  }, error = function(e) {
    message("  Could not extract C&S event study: ", e$message)
    NULL
  })

  if (!is.null(cs_att) && nrow(cs_att) > 0) {
    p_cs <- ggplot(cs_att, aes(x = period, y = ATT)) +
      geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
      geom_vline(xintercept = -0.5, linetype = "dotted", color = "gray40") +
      geom_ribbon(aes(ymin = CI.lower, ymax = CI.upper),
                  alpha = 0.2, fill = "steelblue") +
      geom_line(color = "steelblue") +
      geom_point(size = 1.5, color = "steelblue") +
      labs(x = "Periods Relative to Treatment",
           y = "ATT (Incivility Rate)",
           title = paste0("Event Study (C&S): ", fig$name)) +
      theme_minimal(base_size = 12) +
      theme(plot.title = element_text(face = "bold"))

    save_figure(p_cs, paste0("fig_cs_eventstudy_", fig_key), width = 9, height = 5)
    message("  Saved: fig_cs_eventstudy_", fig_key)
  }

  rm(res_cs); gc()
}
```

## Per-figure coverage intensity maps

```{r coverage-maps}
for (fig_key in names(FIGURES)) {
  fig <- FIGURES[[fig_key]]
  panel_path <- file.path(DATA_PANELS, paste0("did_panel_", fig_key, ".parquet"))

  if (!file.exists(panel_path)) {
    message("No panel for ", fig$name, ", skipping map.")
    next
  }

  message("Generating coverage map for: ", fig$name)

  panel <- as.data.table(read_parquet(panel_path))

  # Per-newspaper coverage info
  np_info <- panel[, .(
    ever_treated = max(as.integer(!is.na(treat_date)), na.rm = TRUE),
    total_figure_articles = sum(figure_count, na.rm = TRUE)
  ), by = newspaper_name]

  # Merge with state mapping
  np_info <- merge(np_info, np_states[, .(newspaper_name, state)],
                   by = "newspaper_name", all.x = TRUE)

  # Fuzzy match for unmatched
  unmatched <- np_info[is.na(state)]
  if (nrow(unmatched) > 0) {
    for (i in seq_len(nrow(unmatched))) {
      short_nm <- unmatched$newspaper_name[i]
      matches <- np_states[startsWith(newspaper_name, short_nm)]
      if (nrow(matches) > 0) {
        np_info[newspaper_name == short_nm, state := matches$state[1]]
      }
    }
  }

  # State-level summary
  state_summary <- np_info[!is.na(state), .(
    n_treated = sum(ever_treated == 1),
    n_control = sum(ever_treated == 0),
    total_articles = sum(total_figure_articles[ever_treated == 1])
  ), by = state]

  state_summary[, intensity := fifelse(
    total_articles == 0, "None",
    fifelse(total_articles <= 25, "Low (1\u201325)",
    fifelse(total_articles <= 75, "Medium (26\u201375)",
            "High (76+)"))
  )]
  state_summary[, intensity := factor(intensity,
    levels = c("None", "Low (1\u201325)", "Medium (26\u201375)", "High (76+)")
  )]

  p_map <- plot_usmap(
    data = state_summary, values = "intensity",
    regions = "states", labels = FALSE
  ) +
    scale_fill_manual(
      values = c("None" = "grey90",
                 "Low (1\u201325)" = "#FFCDD2",
                 "Medium (26\u201375)" = "#E53935",
                 "High (76+)" = "#B71C1C"),
      na.value = "grey90",
      name = paste0(fig$name, "\nArticles")
    ) +
    labs(title = paste0("Coverage Intensity: ", fig$name),
         subtitle = paste0("Study window: ", fig$study_start, "\u2013", fig$study_end)) +
    theme(
      legend.position = "right",
      plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
      plot.subtitle = element_text(size = 10, hjust = 0.5, color = "gray30"),
      legend.text = element_text(size = 10),
      legend.title = element_text(size = 11)
    )

  save_figure(p_map, paste0("fig_coverage_map_", fig_key), width = 10, height = 6)
  message("  Saved: fig_coverage_map_", fig_key)

  rm(panel, np_info, state_summary); gc()
}
```

## Per-figure incivility time series (treated vs control)

```{r timeseries-plots}
for (fig_key in names(FIGURES)) {
  fig <- FIGURES[[fig_key]]
  panel_path <- file.path(DATA_PANELS, paste0("did_panel_", fig_key, ".parquet"))

  if (!file.exists(panel_path)) {
    message("No panel for ", fig$name, ", skipping time series.")
    next
  }

  message("Generating time series for: ", fig$name)

  panel <- as.data.table(read_parquet(panel_path))
  panel[, ever_treated := as.integer(!is.na(treat_date))]

  ts_data <- panel[, .(
    incivil_treated = mean(incivil_rate_rf[ever_treated == 1], na.rm = TRUE),
    incivil_control = mean(incivil_rate_rf[ever_treated == 0], na.rm = TRUE)
  ), by = year_month]

  ts_data[, ym_date := as.Date(paste0(year_month, "-01"))]
  setorder(ts_data, ym_date)

  # Use figure's study window for plot range
  ts_plot_data <- ts_data[
    ym_date >= as.Date(paste0(fig$study_start, "-01-01")) &
    ym_date <= as.Date(paste0(fig$study_end, "-12-31"))
  ]

  if (nrow(ts_plot_data) > 0) {
    p_ts <- ggplot(ts_plot_data, aes(x = ym_date)) +
      geom_line(aes(y = incivil_treated, color = "Treated"), alpha = 0.7) +
      geom_line(aes(y = incivil_control, color = "Control"), alpha = 0.7) +
      scale_color_manual(values = c("Treated" = "firebrick", "Control" = "steelblue")) +
      labs(x = "Date", y = "Mean Incivility Rate",
           title = paste0("Incivility: Treated vs Control — ", fig$name),
           color = "Group") +
      theme_minimal(base_size = 12) +
      theme(plot.title = element_text(face = "bold"))

    save_figure(p_ts, paste0("fig_timeseries_", fig_key), width = 9, height = 5)
    message("  Saved: fig_timeseries_", fig_key)
  }

  rm(panel, ts_data); gc()
}
```

## RF model figures (copy to Overleaf)

```{r rf-figures}
# These are generated in 05_random_forest.Rmd; just copy to Overleaf
for (fig_name in c("rf_variable_importance", "rf_calibration")) {
  for (ext in c("pdf", "png")) {
    src <- file.path(FIGURES_DIR, paste0(fig_name, ".", ext))
    if (file.exists(src)) {
      file.copy(src, file.path(OVERLEAF_FIGURES, paste0(fig_name, ".", ext)),
                overwrite = TRUE)
    }
  }
}
message("RF model figures copied to Overleaf.")
```

## Cross-figure ATT forest plot

```{r forest-plot}
if (length(forest_data) > 0) {
  forest_dt <- rbindlist(forest_data)
  forest_dt[, figure := factor(figure, levels = rev(figure))]

  p_forest <- ggplot(forest_dt, aes(x = att, y = figure)) +
    geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
    geom_point(size = 3, color = "firebrick") +
    geom_errorbarh(aes(xmin = ci_lo, xmax = ci_hi), height = 0.25,
                   color = "firebrick") +
    labs(x = "ATT (IFE Estimator)",
         y = NULL,
         title = "ATT Comparison Across Political Figures",
         subtitle = "Interactive Fixed Effects estimator with 95% CI") +
    theme_minimal(base_size = 12) +
    theme(
      plot.title = element_text(face = "bold", size = 14),
      plot.subtitle = element_text(color = "gray40"),
      axis.text.y = element_text(size = 11)
    )

  save_figure(p_forest, "fig_forest_att_comparison", width = 10, height = 7)
  print(p_forest)
  message("Cross-figure forest plot saved.")
} else {
  message("No IFE models found — forest plot skipped.")
}
```

## Cross-figure summary table

```{r cross-figure-table}
if (length(forest_data) > 0) {
  summary_dt <- rbindlist(forest_data)

  # Add p-values
  summary_dt[, p_value := 2 * pnorm(-abs(att / se))]
  summary_dt[, `:=`(
    ATT     = sprintf("%.4f", att),
    SE      = sprintf("%.4f", se),
    CI      = paste0("[", sprintf("%.4f", ci_lo), ", ", sprintf("%.4f", ci_hi), "]"),
    p       = ifelse(p_value < 0.001, "$<$0.001", sprintf("%.3f", p_value))
  )]

  tex_lines <- c(
    "\\begin{table}[htbp]",
    "\\caption{IFE ATT Estimates Across All Political Figures\\label{tab:cross-figure}}",
    "\\centering",
    "\\begin{tabular}{lcccc}",
    "\\toprule",
    "Figure & ATT & SE & 95\\% CI & $p$-value \\\\",
    "\\midrule"
  )

  for (i in seq_len(nrow(summary_dt))) {
    tex_lines <- c(tex_lines,
      paste0(summary_dt$figure[i], " & ",
             summary_dt$ATT[i], " & ",
             summary_dt$SE[i], " & ",
             summary_dt$CI[i], " & ",
             summary_dt$p[i], " \\\\")
    )
  }

  tex_lines <- c(tex_lines,
    "\\bottomrule",
    "\\end{tabular}",
    "\\\\[2pt]",
    "\\footnotesize\\textit{Note:} ATT estimated via Interactive Fixed Effects (IFE) ",
    "with bootstrap standard errors (200 replications).",
    "\\end{table}"
  )

  tex_string <- paste(tex_lines, collapse = "\n")
  save_table(tex_string, "table_cross_figure_ife")
  message("Cross-figure IFE summary table saved.")
  cat(tex_string, "\n")
} else {
  message("No IFE models found — cross-figure table skipped.")
}
```

## Aggregate incivility over time — national, regional, and state-level

```{r load-all-rf-scored}
# Load all RF-scored articles and compute yearly incivility by newspaper
rf_scored_dir <- file.path(DATA_PANELS, "rf_scored")
rf_files <- list.files(rf_scored_dir, pattern = "\\.parquet$", full.names = TRUE)

if (length(rf_files) > 0) {
  message("Loading ", length(rf_files), " RF-scored year files for aggregate plots...")

  yearly_np <- list()
  for (rf_f in rf_files) {
    yr <- gsub(".*rf_scored_(\\d{4})\\.parquet", "\\1", rf_f)
    dt_yr <- as.data.table(read_parquet(rf_f,
      col_select = c("newspaper_name", "year", "p_incivil")))
    # Aggregate to newspaper x year
    agg <- dt_yr[, .(
      mean_incivil = mean(p_incivil, na.rm = TRUE),
      n_articles = .N
    ), by = .(newspaper_name, year)]
    yearly_np[[yr]] <- agg
    rm(dt_yr, agg); gc()
  }

  np_year <- rbindlist(yearly_np)
  rm(yearly_np); gc()
  message("Aggregate data: ", nrow(np_year), " newspaper-year observations, ",
          uniqueN(np_year$newspaper_name), " newspapers, ",
          uniqueN(np_year$year), " years")

  # Merge with state mapping
  np_year <- merge(np_year, np_states[, .(newspaper_name, state)],
                   by = "newspaper_name", all.x = TRUE)

  # Fuzzy match for unmatched
  unmatched_agg <- np_year[is.na(state), unique(newspaper_name)]
  if (length(unmatched_agg) > 0) {
    for (short_nm in unmatched_agg) {
      matches <- np_states[startsWith(newspaper_name, short_nm)]
      if (nrow(matches) > 0) {
        np_year[newspaper_name == short_nm, state := matches$state[1]]
      }
    }
  }

  message("Newspapers with state match: ",
          uniqueN(np_year[!is.na(state), newspaper_name]), " / ",
          uniqueN(np_year$newspaper_name))

  # Define Census regions
  np_year[, region := fcase(
    state %in% c("CT","ME","MA","NH","RI","VT","NJ","NY","PA"), "Northeast",
    state %in% c("IL","IN","IA","KS","MI","MN","MO","NE","ND","OH","SD","WI"), "Midwest",
    state %in% c("AL","AR","DE","FL","GA","KY","LA","MD","MS","NC","OK","SC",
                 "TN","TX","VA","WV","DC"), "South",
    state %in% c("AZ","CO","ID","MT","NV","NM","OR","UT","WA","WY","CA","AK","HI"), "West",
    default = NA_character_
  )]
} else {
  message("No RF-scored files found — skipping aggregate incivility plots.")
  np_year <- NULL
}
```

### Figure: National incivility trend

```{r fig-national-incivility}
if (!is.null(np_year) && nrow(np_year) > 0) {
  # Weighted mean incivility per year (weighted by article count)
  national <- np_year[, .(
    mean_incivil = weighted.mean(mean_incivil, n_articles, na.rm = TRUE),
    n_newspapers = uniqueN(newspaper_name),
    n_articles = sum(n_articles)
  ), by = year]
  setorder(national, year)

  p_national <- ggplot(national, aes(x = year, y = mean_incivil)) +
    geom_line(color = "firebrick", linewidth = 0.8) +
    geom_smooth(method = "loess", span = 0.15, se = TRUE,
                color = "gray30", fill = "gray80", alpha = 0.3) +
    labs(x = "Year", y = "Mean Incivility (RF Score)",
         title = "Newspaper Incivility in the United States, 1774\u20131960",
         subtitle = "Article-weighted annual average across all newspapers") +
    theme_minimal(base_size = 12) +
    theme(
      plot.title = element_text(face = "bold", size = 14),
      plot.subtitle = element_text(color = "gray40")
    )

  save_figure(p_national, "fig_national_incivility_trend", width = 10, height = 6)
  print(p_national)
  message("National incivility trend saved.")
}
```

### Figure: Incivility by Census region over time

```{r fig-regional-incivility}
if (!is.null(np_year) && nrow(np_year[!is.na(region)]) > 0) {
  regional <- np_year[!is.na(region), .(
    mean_incivil = weighted.mean(mean_incivil, n_articles, na.rm = TRUE),
    n_newspapers = uniqueN(newspaper_name),
    n_articles = sum(n_articles)
  ), by = .(year, region)]
  setorder(regional, region, year)

  # Filter to regions with reasonable coverage (at least 3 newspapers in a year)
  regional <- regional[n_newspapers >= 3]

  p_region <- ggplot(regional, aes(x = year, y = mean_incivil, color = region)) +
    geom_line(alpha = 0.4, linewidth = 0.4) +
    geom_smooth(method = "loess", span = 0.2, se = FALSE, linewidth = 1) +
    scale_color_manual(values = c(
      "Northeast" = "#1b9e77",
      "Midwest"   = "#d95f02",
      "South"     = "#7570b3",
      "West"      = "#e7298a"
    )) +
    labs(x = "Year", y = "Mean Incivility (RF Score)",
         title = "Newspaper Incivility by U.S. Census Region",
         subtitle = "Smoothed trends; regions with \u22653 newspapers per year",
         color = "Region") +
    theme_minimal(base_size = 12) +
    theme(
      plot.title = element_text(face = "bold", size = 14),
      plot.subtitle = element_text(color = "gray40"),
      legend.position = "bottom"
    )

  save_figure(p_region, "fig_regional_incivility_trend", width = 10, height = 6)
  print(p_region)
  message("Regional incivility trend saved.")
}
```

### Figure: Incivility by state over time

```{r fig-state-incivility, fig.width=12, fig.height=10}
if (!is.null(np_year) && nrow(np_year[!is.na(state)]) > 0) {
  state_year <- np_year[!is.na(state), .(
    mean_incivil = weighted.mean(mean_incivil, n_articles, na.rm = TRUE),
    n_newspapers = uniqueN(newspaper_name),
    n_articles = sum(n_articles)
  ), by = .(year, state, region)]
  setorder(state_year, state, year)

  # Keep only states with at least 10 years of data and at least 2 newspapers on avg
  state_coverage <- state_year[, .(
    n_years = uniqueN(year),
    avg_np = mean(n_newspapers)
  ), by = state]
  keep_states <- state_coverage[n_years >= 10 & avg_np >= 2, state]
  state_plot <- state_year[state %in% keep_states]

  message("States with sufficient coverage: ", length(keep_states),
          " out of ", uniqueN(state_year$state))

  if (nrow(state_plot) > 0) {
    # Add region for faceting color
    state_plot[, region := fcase(
      state %in% c("CT","ME","MA","NH","RI","VT","NJ","NY","PA"), "Northeast",
      state %in% c("IL","IN","IA","KS","MI","MN","MO","NE","ND","OH","SD","WI"), "Midwest",
      state %in% c("AL","AR","DE","FL","GA","KY","LA","MD","MS","NC","OK","SC",
                   "TN","TX","VA","WV","DC"), "South",
      state %in% c("AZ","CO","ID","MT","NV","NM","OR","UT","WA","WY","CA","AK","HI"), "West",
      default = "Other"
    )]

    p_state <- ggplot(state_plot, aes(x = year, y = mean_incivil,
                                       color = region, group = state)) +
      geom_line(alpha = 0.6, linewidth = 0.5) +
      facet_wrap(~ state, scales = "free_y", ncol = 6) +
      scale_color_manual(values = c(
        "Northeast" = "#1b9e77",
        "Midwest"   = "#d95f02",
        "South"     = "#7570b3",
        "West"      = "#e7298a",
        "Other"     = "gray50"
      )) +
      labs(x = "Year", y = "Incivility",
           title = "Newspaper Incivility by State",
           subtitle = "States with \u226510 years of data and \u22652 newspapers on average",
           color = "Region") +
      theme_minimal(base_size = 9) +
      theme(
        plot.title = element_text(face = "bold", size = 14),
        plot.subtitle = element_text(color = "gray40", size = 10),
        strip.text = element_text(face = "bold", size = 8),
        axis.text.x = element_text(angle = 45, hjust = 1, size = 6),
        axis.text.y = element_text(size = 6),
        legend.position = "bottom",
        panel.spacing = unit(0.3, "lines")
      )

    save_figure(p_state, "fig_state_incivility_trend", width = 14, height = 10)
    print(p_state)
    message("State-level incivility trend saved.")
  }
}
```

## Export: newspaper-level incivility summary CSV

```{r newspaper-csv}
if (!is.null(np_year) && nrow(np_year) > 0) {
  newspaper_summary <- np_year[, .(
    state          = state[1],
    region         = region[1],
    first_year     = min(year),
    last_year      = max(year),
    n_years        = uniqueN(year),
    total_articles = sum(n_articles),
    mean_incivil   = round(weighted.mean(mean_incivil, n_articles, na.rm = TRUE), 6),
    sd_incivil     = round(sd(rep(mean_incivil, n_articles), na.rm = TRUE), 6),
    min_incivil    = round(min(mean_incivil, na.rm = TRUE), 6),
    max_incivil    = round(max(mean_incivil, na.rm = TRUE), 6)
  ), by = newspaper_name]

  setorder(newspaper_summary, -mean_incivil)

  csv_path <- file.path(DATA_PANELS, "newspaper_incivility_summary.csv")
  write.csv(newspaper_summary, csv_path, row.names = FALSE)
  message("Saved newspaper summary: ", csv_path,
          " (", nrow(newspaper_summary), " newspapers)")

  # Quick stats
  message("  Mean incivility across newspapers: ",
          round(mean(newspaper_summary$mean_incivil, na.rm = TRUE), 4))
  message("  Most incivil: ", newspaper_summary$newspaper_name[1],
          " (", newspaper_summary$mean_incivil[1], ")")
  message("  Least incivil: ", newspaper_summary$newspaper_name[nrow(newspaper_summary)],
          " (", newspaper_summary$mean_incivil[nrow(newspaper_summary)], ")")
}
```

## Final file listing

```{r file-listing}
message("\n=== Files in Overleaf Figures ===")
cat(paste(list.files(OVERLEAF_FIGURES), collapse = "\n"), "\n")

message("\n=== Files in Overleaf Tables ===")
cat(paste(list.files(OVERLEAF_TABLES), collapse = "\n"), "\n")

message("\n=== Files in local figures/ ===")
cat(paste(list.files(FIGURES_DIR), collapse = "\n"), "\n")

message("\n=== Files in local tables/ ===")
cat(paste(list.files(TABLES_DIR), collapse = "\n"), "\n")

message("\nAll figures and tables exported successfully.")
```
