---
title: "08 — Publication Figures and Tables"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = TRUE, warning = TRUE,
                      fig.width = 8, fig.height = 6, dpi = 300)
knitr::opts_knit$set(root.dir = "C:/Users/ammonsj/Ideas")
source("C:/Users/ammonsj/Ideas/_config.R")
```

## Load models and data

```{r load}
library(data.table)
library(arrow)
library(ggplot2)
library(patchwork)
library(fect)

# Load fect models
out_ife     <- readRDS(file.path(MODELS_DIR, "fect_ife.rds"))
out_mc      <- readRDS(file.path(MODELS_DIR, "fect_mc.rds"))
out_fe      <- readRDS(file.path(MODELS_DIR, "fect_fe.rds"))
out_placebo <- readRDS(file.path(MODELS_DIR, "fect_placebo.rds"))
out_carry   <- readRDS(file.path(MODELS_DIR, "fect_carryover.rds"))
out_ife_lex <- readRDS(file.path(MODELS_DIR, "fect_ife_lexicon.rds"))

# Load panel
panel <- as.data.table(read_parquet(
  file.path(DATA_PANELS, "did_panel.parquet")
))

message("All models and data loaded.")
```

## Figure 1: IFE ATT Dynamic Plot

```{r fig-ife-att}
pdf(file.path(FIGURES_DIR, "fig1_ife_att.pdf"), width = 8, height = 6)
plot(out_ife, main = "ATT Estimates: Interactive Fixed Effects",
     ylab = "ATT (Incivility Rate)", xlab = "Periods Since Treatment",
     cex.main = 1.2, cex.lab = 1.1)
dev.off()

png(file.path(FIGURES_DIR, "fig1_ife_att.png"), width = 8, height = 6,
    units = "in", res = 300)
plot(out_ife, main = "ATT Estimates: Interactive Fixed Effects",
     ylab = "ATT (Incivility Rate)", xlab = "Periods Since Treatment",
     cex.main = 1.2, cex.lab = 1.1)
dev.off()

# Copy to Overleaf
file.copy(file.path(FIGURES_DIR, "fig1_ife_att.pdf"),
          file.path(OVERLEAF_FIGURES, "fig1_ife_att.pdf"), overwrite = TRUE)
file.copy(file.path(FIGURES_DIR, "fig1_ife_att.png"),
          file.path(OVERLEAF_FIGURES, "fig1_ife_att.png"), overwrite = TRUE)

message("Figure 1 saved.")
```

## Figure 2: Placebo Test

```{r fig-placebo}
pdf(file.path(FIGURES_DIR, "fig2_placebo_test.pdf"), width = 8, height = 6)
plot(out_placebo, main = "Placebo Test (Pre-Treatment Periods)",
     ylab = "ATT (Incivility Rate)", xlab = "Periods Since Treatment",
     cex.main = 1.2, cex.lab = 1.1)
dev.off()

png(file.path(FIGURES_DIR, "fig2_placebo_test.png"), width = 8, height = 6,
    units = "in", res = 300)
plot(out_placebo, main = "Placebo Test (Pre-Treatment Periods)",
     ylab = "ATT (Incivility Rate)", xlab = "Periods Since Treatment",
     cex.main = 1.2, cex.lab = 1.1)
dev.off()

file.copy(file.path(FIGURES_DIR, "fig2_placebo_test.pdf"),
          file.path(OVERLEAF_FIGURES, "fig2_placebo_test.pdf"), overwrite = TRUE)
file.copy(file.path(FIGURES_DIR, "fig2_placebo_test.png"),
          file.path(OVERLEAF_FIGURES, "fig2_placebo_test.png"), overwrite = TRUE)

message("Figure 2 saved.")
```

## Figure 3: Carryover Test (Persistence / Equilibrium Shift)

```{r fig-carryover}
pdf(file.path(FIGURES_DIR, "fig3_carryover_test.pdf"), width = 8, height = 6)
plot(out_carry, main = "Carryover Test (Effect Persistence)",
     ylab = "ATT (Incivility Rate)", xlab = "Periods Since Treatment",
     cex.main = 1.2, cex.lab = 1.1)
dev.off()

png(file.path(FIGURES_DIR, "fig3_carryover_test.png"), width = 8, height = 6,
    units = "in", res = 300)
plot(out_carry, main = "Carryover Test (Effect Persistence)",
     ylab = "ATT (Incivility Rate)", xlab = "Periods Since Treatment",
     cex.main = 1.2, cex.lab = 1.1)
dev.off()

file.copy(file.path(FIGURES_DIR, "fig3_carryover_test.pdf"),
          file.path(OVERLEAF_FIGURES, "fig3_carryover_test.pdf"), overwrite = TRUE)
file.copy(file.path(FIGURES_DIR, "fig3_carryover_test.png"),
          file.path(OVERLEAF_FIGURES, "fig3_carryover_test.png"), overwrite = TRUE)

message("Figure 3 saved.")
```

## Figure 4: Matrix Completion vs IFE Comparison

```{r fig-comparison}
pdf(file.path(FIGURES_DIR, "fig4_mc_comparison.pdf"), width = 10, height = 5)
par(mfrow = c(1, 2))
plot(out_ife, main = "IFE", ylab = "ATT", xlab = "Periods",
     cex.main = 1.1, cex.lab = 1.0)
plot(out_mc, main = "Matrix Completion", ylab = "ATT", xlab = "Periods",
     cex.main = 1.1, cex.lab = 1.0)
dev.off()

png(file.path(FIGURES_DIR, "fig4_mc_comparison.png"), width = 10, height = 5,
    units = "in", res = 300)
par(mfrow = c(1, 2))
plot(out_ife, main = "IFE", ylab = "ATT", xlab = "Periods",
     cex.main = 1.1, cex.lab = 1.0)
plot(out_mc, main = "Matrix Completion", ylab = "ATT", xlab = "Periods",
     cex.main = 1.1, cex.lab = 1.0)
dev.off()

file.copy(file.path(FIGURES_DIR, "fig4_mc_comparison.pdf"),
          file.path(OVERLEAF_FIGURES, "fig4_mc_comparison.pdf"), overwrite = TRUE)
file.copy(file.path(FIGURES_DIR, "fig4_mc_comparison.png"),
          file.path(OVERLEAF_FIGURES, "fig4_mc_comparison.png"), overwrite = TRUE)

message("Figure 4 saved.")
```

## Figure 5: Incivility Time Series (Treated vs Control)

```{r fig-timeseries}
panel[, ever_treated := as.integer(!is.na(treat_date))]

ts_data <- panel[, .(
  incivil_treated = mean(incivil_rate_rf[ever_treated == 1], na.rm = TRUE),
  incivil_control = mean(incivil_rate_rf[ever_treated == 0], na.rm = TRUE)
), by = year_month]

ts_data[, ym_date := as.Date(paste0(year_month, "-01"))]
setorder(ts_data, ym_date)

# Only plot study window (1920-1945) for clarity
ts_plot_data <- ts_data[ym_date >= as.Date("1920-01-01") &
                        ym_date <= as.Date("1945-01-01")]

if (nrow(ts_plot_data) > 0) {
  p_ts <- ggplot(ts_plot_data, aes(x = ym_date)) +
    geom_line(aes(y = incivil_treated, color = "Treated"), alpha = 0.7) +
    geom_line(aes(y = incivil_control, color = "Control"), alpha = 0.7) +
    geom_vline(xintercept = as.Date("1936-01-01"),
               linetype = "dashed", color = "gray40") +
    annotate("text", x = as.Date("1936-06-01"), y = Inf,
             label = "Coughlin peak", vjust = 2, size = 3) +
    scale_color_manual(values = c("Treated" = "firebrick", "Control" = "steelblue")) +
    labs(x = "Date", y = "Mean Incivility Rate",
         title = "Newspaper Incivility: Treated vs Control",
         color = "Group") +
    theme_minimal(base_size = 12)

  save_figure(p_ts, "fig5_timeseries", width = 9, height = 5)
  print(p_ts)
} else {
  message("No data in 1920-1945 window for time series plot.")
}
```

## Figure 6: RF Variable Importance

This was already created in 05_random_forest.Rmd but we copy to Overleaf.

```{r fig-rf-importance}
# Copy if exists
for (ext in c("pdf", "png")) {
  src <- file.path(FIGURES_DIR, paste0("rf_variable_importance.", ext))
  if (file.exists(src)) {
    file.copy(src, file.path(OVERLEAF_FIGURES,
              paste0("fig6_rf_importance.", ext)), overwrite = TRUE)
  }
}
message("Figure 6 (RF importance) copied to Overleaf.")
```

## Figure 7: RF Calibration

```{r fig-rf-calibration}
for (ext in c("pdf", "png")) {
  src <- file.path(FIGURES_DIR, paste0("rf_calibration.", ext))
  if (file.exists(src)) {
    file.copy(src, file.path(OVERLEAF_FIGURES,
              paste0("fig7_rf_calibration.", ext)), overwrite = TRUE)
  }
}
message("Figure 7 (RF calibration) copied to Overleaf.")
```

## Table: Main Results

```{r table-main}
# Extract ATT from each model
extract_att <- function(model, label) {
  att <- model$att.avg
  se <- model$att.avg.se
  data.table(
    Model = label,
    ATT = round(att, 4),
    SE = round(se, 4),
    `95% CI` = paste0("[", round(att - 1.96*se, 4), ", ", round(att + 1.96*se, 4), "]"),
    `p-value` = round(2 * pnorm(-abs(att / se)), 4)
  )
}

results <- rbindlist(list(
  extract_att(out_ife, "IFE (primary)"),
  extract_att(out_mc, "Matrix Completion"),
  extract_att(out_fe, "Two-Way FE"),
  extract_att(out_ife_lex, "IFE (lexicon outcome)")
))

tex <- knitr::kable(results, format = "latex", booktabs = TRUE,
                    caption = "Estimated ATT: Effect of Coughlin Exposure on Newspaper Incivility")

for (dir in c(TABLES_DIR, OVERLEAF_TABLES)) {
  writeLines(tex, file.path(dir, "main_results.tex"))
}
message("Main results table saved.")
print(results)
```

## Table: Robustness

```{r table-robustness}
# Robustness specifications
rob_results <- rbindlist(list(
  extract_att(out_ife, "IFE — RF outcome"),
  extract_att(out_ife_lex, "IFE — Lexicon outcome")
))

tex_rob <- knitr::kable(rob_results, format = "latex", booktabs = TRUE,
                        caption = "Robustness: Alternative Outcome Measures")

for (dir in c(TABLES_DIR, OVERLEAF_TABLES)) {
  writeLines(tex_rob, file.path(dir, "robustness.tex"))
}
message("Robustness table saved.")
```

## Final file listing

```{r file-listing}
message("\n=== Files in Overleaf Figures ===")
cat(list.files(OVERLEAF_FIGURES), sep = "\n")

message("\n=== Files in Overleaf Tables ===")
cat(list.files(OVERLEAF_TABLES), sep = "\n")

message("\nAll figures and tables exported successfully.")
```
