---
title: "08 — Publication Figures and Tables (Multi-Figure)"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = TRUE, warning = TRUE,
                      fig.width = 8, fig.height = 6, dpi = 300)
knitr::opts_knit$set(root.dir = "C:/Users/ammonsj/Ideas")
source("C:/Users/ammonsj/Ideas/_config.R")
```

```{r libraries}
library(data.table)
library(arrow)
library(ggplot2)
library(patchwork)
library(fect)
library(usmap)
library(knitr)
```

## Helper functions

```{r helpers}
# Extract ATT from fect models (bootstrap SE)
extract_fect_att <- function(model) {
  att <- as.numeric(model$att.avg)
  # Defensive: check that bootstrap output exists before computing SE
  se <- if (!is.null(model$att.avg.boot) && length(model$att.avg.boot) > 1) {
    sd(model$att.avg.boot)
  } else {
    NA_real_
  }
  list(att = att, se = se,
       ci_lo = att - 1.96 * se, ci_hi = att + 1.96 * se,
       p = 2 * pnorm(-abs(att / se)))
}

# Extract ATT from did_wrapper models
extract_did_att <- function(model) {
  avg <- model$est.avg
  if (is.null(avg)) return(list(att = NA_real_, se = NA_real_,
                                 ci_lo = NA_real_, ci_hi = NA_real_, p = NA_real_))
  null_to_na <- function(x) if (is.null(x)) NA_real_ else x
  list(att = null_to_na(avg$ATT.avg), se = null_to_na(avg$S.E.),
       ci_lo = null_to_na(avg$CI.lower), ci_hi = null_to_na(avg$CI.upper),
       p = null_to_na(avg$p.value))
}

# Format a coefficient cell: "coef\n(se)"
fmt_coef <- function(att, se) {
  if (is.na(att)) return("")
  paste0(sprintf("%.4f", att), "\n(", sprintf("%.4f", se), ")")
}

# Format CI
fmt_ci <- function(lo, hi) {
  if (is.na(lo)) return("")
  paste0("[", sprintf("%.4f", lo), ", ", sprintf("%.4f", hi), "]")
}

# Format p-value
fmt_p <- function(p) {
  if (is.na(p)) return("")
  if (p < 0.001) return("$<$0.001")
  sprintf("%.3f", p)
}

# Load newspaper-to-state mapping for maps (optional — maps/regional plots need this)
np_states_path <- file.path(DATA_PANELS, "newspaper_states.csv")
HAS_NP_STATES <- file.exists(np_states_path)
if (HAS_NP_STATES) {
  np_states <- fread(np_states_path, encoding = "UTF-8")
  np_states <- np_states[state != ""]
  message("Loaded ", nrow(np_states), " newspaper-state mappings.")
} else {
  np_states <- data.table(newspaper_name = character(), state = character())
  message("WARNING: newspaper_states.csv not found. Coverage maps and regional plots will be skipped.")
}
```

## Per-figure horizontal results tables

```{r horizontal-tables}
# --- Significance stars ---
sig_stars <- function(p) {
  if (is.na(p)) return("")
  if (p < 0.001) return("$^{***}$")
  if (p < 0.01) return("$^{**}$")
  if (p < 0.05) return("$^{*}$")
  return("")
}

# Store ATTs for cross-figure forest plot
forest_data <- list()

for (fig_key in names(FIGURES)) {
  fig <- FIGURES[[fig_key]]
  message("\n", strrep("=", 60))
  message("Building table for: ", fig$name, " (", fig_key, ")")
  message(strrep("=", 60))

  # --- Load panel for observation counts ---
  panel_path <- file.path(DATA_PANELS, paste0("did_panel_", fig_key, ".parquet"))
  if (!file.exists(panel_path)) {
    message("  No panel for ", fig$name, ", skipping.")
    next
  }
  panel <- as.data.table(read_parquet(panel_path))
  n_obs <- nrow(panel)
  n_units <- uniqueN(panel$newspaper_id)
  n_treated_units <- uniqueN(panel[!is.na(treat_date), newspaper_id])
  n_control_units <- n_units - n_treated_units
  n_time_periods <- uniqueN(panel$time_id)

  # --- Collect estimates from 3 models: TWFE(Imp.), MC, dCDH(Switcher) ---
  model_specs <- list(
    fe = list(
      file = paste0("fect_fe_", fig_key, ".rds"),
      label = "TWFE (Imp.)",
      type = "fect"
    ),
    mc = list(
      file = paste0("fect_mc_", fig_key, ".rds"),
      label = "MC",
      type = "fect"
    ),
    didm_sw = list(
      file = paste0("did_didm_switcher_", fig_key, ".rds"),
      label = "dCDH",
      type = "did_switcher"
    )
  )

  # Results storage
  att_vals <- se_vals <- ci_lo_vals <- ci_hi_vals <- p_vals <- rep(NA_real_, 3)
  nboots_vals <- rep(NA_integer_, 3)
  mspe_vals <- rep(NA_real_, 3)
  r_cv_vals <- rep(NA_integer_, 3)     # number of factors (MC)
  switcher_n <- switcher_events <- NA_integer_
  p_joint_eff <- p_joint_plac <- NA_real_
  delta_d_avg <- NA_real_
  n_newspapers_ever_treated_sw <- NA_integer_
  names(att_vals) <- names(se_vals) <- names(ci_lo_vals) <- names(ci_hi_vals) <- names(p_vals) <- names(model_specs)

  for (i in seq_along(model_specs)) {
    spec <- model_specs[[i]]
    mkey <- names(model_specs)[i]
    mpath <- file.path(MODELS_DIR, spec$file)

    if (!file.exists(mpath)) {
      message("  ", spec$label, " model not found, skipping.")
      next
    }

    m <- readRDS(mpath)

    if (spec$type == "fect") {
      res <- extract_fect_att(m)
      att_vals[mkey]  <- res$att
      se_vals[mkey]   <- res$se
      ci_lo_vals[mkey] <- res$ci_lo
      ci_hi_vals[mkey] <- res$ci_hi
      p_vals[mkey]    <- res$p
      nboots_vals[i] <- if (!is.null(m$att.avg.boot)) length(m$att.avg.boot) else NA_integer_
      mspe_vals[i] <- if (!is.null(m$MSPE)) as.numeric(m$MSPE) else NA_real_
      r_cv_vals[i] <- if (!is.null(m$r.cv)) as.integer(m$r.cv) else NA_integer_
    } else if (spec$type == "did_switcher") {
      res <- extract_did_att(m)
      att_vals[mkey]  <- res$att
      se_vals[mkey]   <- res$se
      ci_lo_vals[mkey] <- res$ci_lo
      ci_hi_vals[mkey] <- res$ci_hi
      p_vals[mkey]    <- res$p
      # Extract switcher-specific info
      if (!is.null(m$switcher_info)) {
        si <- m$switcher_info
        switcher_n <- si$n_switchers
        switcher_events <- si$n_switch_events
        p_joint_eff <- si$p_jointeffects
        p_joint_plac <- si$p_jointplacebo
        delta_d_avg <- si$delta_D_avg_total
        n_newspapers_ever_treated_sw <- si$n_newspapers_ever_treated
      }
    }

    rm(m); gc()
  }

  # Check if any models were found
  if (all(is.na(att_vals))) {
    message("  No models found for ", fig$name, ", skipping table.")
    rm(panel); gc()
    next
  }

  # Store MC result for forest plot (or TWFE Imp if MC unavailable)
  forest_key <- if (!is.na(att_vals["mc"])) "mc" else "fe"
  if (!is.na(att_vals[forest_key])) {
    forest_data[[fig_key]] <- data.table(
      figure = fig$name,
      att    = att_vals[forest_key],
      se     = se_vals[forest_key],
      ci_lo  = ci_lo_vals[forest_key],
      ci_hi  = ci_hi_vals[forest_key]
    )
  }

  # --- Build LaTeX table with richer statistics ---
  active <- !is.na(att_vals)
  active_keys <- names(model_specs)[active]
  active_labels <- sapply(model_specs[active_keys], `[[`, "label")
  ncols <- sum(active)
  col_spec <- paste(rep("c", ncols), collapse = "")

  tex_lines <- c(
    "\\begin{table}[htbp]",
    paste0("\\caption{ATT Estimates: ", fig$name, "\\label{tab:", fig_key, "-results}}"),
    "\\centering",
    "\\small",
    paste0("\\begin{tabular}{l", col_spec, "}"),
    "\\toprule",
    paste0(" & ", paste(active_labels, collapse = " & "), " \\\\"),
    "\\midrule"
  )

  # Row: ATT with significance stars
  att_cells <- sapply(active_keys, function(k) {
    paste0(sprintf("%.4f", att_vals[k]), sig_stars(p_vals[k]))
  })
  tex_lines <- c(tex_lines,
    paste0("ATT & ", paste(att_cells, collapse = " & "), " \\\\"))

  # Row: (SE)
  se_cells <- sapply(active_keys, function(k) {
    paste0("(", sprintf("%.4f", se_vals[k]), ")")
  })
  tex_lines <- c(tex_lines,
    paste0(" & ", paste(se_cells, collapse = " & "), " \\\\"))

  # Row: 95% CI
  ci_cells <- sapply(active_keys, function(k) {
    paste0("[", sprintf("%.4f", ci_lo_vals[k]), ", ", sprintf("%.4f", ci_hi_vals[k]), "]")
  })
  tex_lines <- c(tex_lines,
    paste0("95\\% CI & ", paste(ci_cells, collapse = " & "), " \\\\"))

  # Separator before diagnostics
  tex_lines <- c(tex_lines, "\\midrule")

  # Row: Observations
  obs_cells <- sapply(active_keys, function(k) {
    formatC(n_obs, format = "d", big.mark = ",")
  })
  tex_lines <- c(tex_lines,
    paste0("Observations & ", paste(obs_cells, collapse = " & "), " \\\\"))

  # Row: Newspapers
  unit_cells <- sapply(active_keys, function(k) {
    formatC(n_units, format = "d", big.mark = ",")
  })
  tex_lines <- c(tex_lines,
    paste0("Newspapers & ", paste(unit_cells, collapse = " & "), " \\\\"))

  # Row: Time periods
  time_cells <- sapply(active_keys, function(k) {
    formatC(n_time_periods, format = "d", big.mark = ",")
  })
  tex_lines <- c(tex_lines,
    paste0("Time periods & ", paste(time_cells, collapse = " & "), " \\\\"))

  # Row: Treated units / Switchers
  treat_cells <- sapply(active_keys, function(k) {
    spec <- model_specs[[k]]
    if (spec$type == "did_switcher" && !is.na(switcher_n)) {
      formatC(switcher_n, format = "d", big.mark = ",")
    } else {
      formatC(n_treated_units, format = "d", big.mark = ",")
    }
  })
  treat_row_label <- if ("didm_sw" %in% active_keys) {
    "Treated / Switchers"
  } else {
    "Treated units"
  }
  tex_lines <- c(tex_lines,
    paste0(treat_row_label, " & ", paste(treat_cells, collapse = " & "), " \\\\"))

  # Row: Switch events (dCDH only, blank for others)
  if ("didm_sw" %in% active_keys && !is.na(switcher_events)) {
    sw_cells <- sapply(active_keys, function(k) {
      if (k == "didm_sw") formatC(switcher_events, format = "d", big.mark = ",") else "---"
    })
    tex_lines <- c(tex_lines,
      paste0("Switch events & ", paste(sw_cells, collapse = " & "), " \\\\"))
  }

  # Row: Never-treated units
  control_cells <- sapply(active_keys, function(k) {
    formatC(n_control_units, format = "d", big.mark = ",")
  })
  tex_lines <- c(tex_lines,
    paste0("Never-treated & ", paste(control_cells, collapse = " & "), " \\\\"))

  # Separator before model diagnostics
  tex_lines <- c(tex_lines, "\\midrule")

  # Row: Treatment definition
  tdef_cells <- sapply(active_keys, function(k) {
    spec <- model_specs[[k]]
    if (spec$type == "did_switcher") "Article pub." else "Sust.\\ coverage"
  })
  tex_lines <- c(tex_lines,
    paste0("Treatment & ", paste(tdef_cells, collapse = " & "), " \\\\"))

  # Row: SE method
  se_method_cells <- sapply(active_keys, function(k) {
    spec <- model_specs[[k]]
    if (spec$type == "fect") "Bootstrap" else "Analytical"
  })
  tex_lines <- c(tex_lines,
    paste0("SE method & ", paste(se_method_cells, collapse = " & "), " \\\\"))

  # Row: Bootstrap replications (fect only)
  any_boots <- any(!is.na(nboots_vals[active]))
  if (any_boots) {
    boot_cells <- sapply(seq_along(active_keys), function(i) {
      idx <- which(names(model_specs) == active_keys[i])
      if (!is.na(nboots_vals[idx])) as.character(nboots_vals[idx]) else "---"
    })
    tex_lines <- c(tex_lines,
      paste0("Bootstrap reps & ", paste(boot_cells, collapse = " & "), " \\\\"))
  }

  # Row: Factors selected (MC only)
  if ("mc" %in% active_keys) {
    mc_idx <- which(names(model_specs) == "mc")
    if (!is.na(r_cv_vals[mc_idx])) {
      fac_cells <- sapply(active_keys, function(k) {
        if (k == "mc") as.character(r_cv_vals[mc_idx]) else "---"
      })
      tex_lines <- c(tex_lines,
        paste0("Factors (CV) & ", paste(fac_cells, collapse = " & "), " \\\\"))
    }
  }

  # Row: Joint effects test (dCDH only)
  if ("didm_sw" %in% active_keys && !is.na(p_joint_eff)) {
    jf_cells <- sapply(active_keys, function(k) {
      if (k == "didm_sw") sprintf("%.3f", p_joint_eff) else "---"
    })
    tex_lines <- c(tex_lines,
      paste0("Joint effects $p$ & ", paste(jf_cells, collapse = " & "), " \\\\"))
  }

  # Row: Joint placebo test (dCDH only)
  if ("didm_sw" %in% active_keys && !is.na(p_joint_plac)) {
    jp_cells <- sapply(active_keys, function(k) {
      if (k == "didm_sw") sprintf("%.3f", p_joint_plac) else "---"
    })
    tex_lines <- c(tex_lines,
      paste0("Joint placebo $p$ & ", paste(jp_cells, collapse = " & "), " \\\\"))
  }

  # Row: Pre-treatment MSPE (fect only)
  any_mspe <- any(!is.na(mspe_vals[active]))
  if (any_mspe) {
    mspe_cells <- sapply(seq_along(active_keys), function(i) {
      idx <- which(names(model_specs) == active_keys[i])
      if (!is.na(mspe_vals[idx])) sprintf("%.6f", mspe_vals[idx]) else "---"
    })
    tex_lines <- c(tex_lines,
      paste0("Pre-treat.\\ MSPE & ", paste(mspe_cells, collapse = " & "), " \\\\"))
  }

  tex_lines <- c(tex_lines,
    "\\bottomrule",
    "\\end{tabular}",
    "\\\\[2pt]",
    paste0("\\footnotesize\\textit{Note:} ",
           "$^{*}p<0.05$, $^{**}p<0.01$, $^{***}p<0.001$. ",
           "Standard errors in parentheses. ",
           "TWFE (Imp.) = Two-Way FE Imputation (Borusyak et al.\\ 2024); ",
           "MC = Matrix Completion (Athey et al.\\ 2021); ",
           "dCDH = de Chaisemartin \\& D'Haultfoeuille (2024), switcher design ",
           "(treatment = published Coughlin article that month). ",
           "``Sust.\\ coverage'' = sustained coverage threshold (\\(\\geq\\)2 of 3 consecutive months ",
           "with \\(\\geq\\)2 figure articles). ",
           "Study window: ", fig$study_start, "--", fig$study_end, "."),
    "\\end{table}"
  )

  tex_string <- paste(tex_lines, collapse = "\n")
  save_table(tex_string, paste0("table_", fig_key, "_results"))
  message("  Saved: table_", fig_key, "_results.tex")
  cat(tex_string, "\n\n")

  rm(panel); gc()
}
```

## Per-figure IFE event study plots

```{r ife-event-studies}
for (fig_key in names(FIGURES)) {
  fig <- FIGURES[[fig_key]]
  model_path <- file.path(MODELS_DIR, paste0("fect_ife_", fig_key, ".rds"))

  if (!file.exists(model_path)) {
    message("No IFE model for ", fig$name, ", skipping plot.")
    next
  }

  message("Generating IFE event study for: ", fig$name)

  out_ife <- readRDS(model_path)

  # fect::plot() returns a ggplot object — use save_figure() for consistent output
  p_ife <- plot(out_ife, main = paste0("ATT: ", fig$name, " (IFE)"),
       ylab = "ATT (Incivility Rate)", xlab = "Periods Since Treatment",
       cex.main = 1.2, cex.lab = 1.1)
  save_figure(p_ife, paste0("fig_ife_att_", fig_key), width = 8, height = 6)

  rm(out_ife); gc()
  message("  Saved: fig_ife_att_", fig_key)
}
```

## Per-figure placebo test plots

```{r placebo-plots}
for (fig_key in names(FIGURES)) {
  fig <- FIGURES[[fig_key]]
  placebo_path <- file.path(MODELS_DIR, paste0("fect_placebo_", fig_key, ".rds"))

  if (!file.exists(placebo_path)) {
    message("No placebo model for ", fig$name, ", skipping.")
    next
  }

  message("Generating placebo plot for: ", fig$name)

  out_placebo <- readRDS(placebo_path)

  # fect::plot() returns a ggplot object — use save_figure() for consistent output
  p_placebo <- plot(out_placebo, main = paste0("Placebo Test: ", fig$name),
       ylab = "ATT (Incivility Rate)", xlab = "Periods Since Treatment",
       cex.main = 1.2, cex.lab = 1.1)
  save_figure(p_placebo, paste0("fig_placebo_", fig_key), width = 8, height = 6)

  rm(out_placebo); gc()
  message("  Saved: fig_placebo_", fig_key)
}
```

## Per-figure C&S event study plots

```{r cs-event-studies}
for (fig_key in names(FIGURES)) {
  fig <- FIGURES[[fig_key]]
  cs_path <- file.path(MODELS_DIR, paste0("did_cs_notyet_", fig_key, ".rds"))

  if (!file.exists(cs_path)) {
    message("No C&S model for ", fig$name, ", skipping.")
    next
  }

  message("Generating C&S event study for: ", fig$name)

  res_cs <- readRDS(cs_path)
  cs_att <- tryCatch({
    # FIXED: est.att already has a 'period' column from did_wrapper.
    # Do NOT use rownames() — that gives sequential indices, not event-time periods.
    dt <- as.data.table(res_cs$est.att)
    dt[period >= -24 & period <= 24]
  }, error = function(e) {
    message("  Could not extract C&S event study: ", e$message)
    NULL
  })

  if (!is.null(cs_att) && nrow(cs_att) > 0) {
    p_cs <- ggplot(cs_att, aes(x = period, y = ATT)) +
      geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
      geom_vline(xintercept = -0.5, linetype = "dotted", color = "gray40") +
      geom_ribbon(aes(ymin = CI.lower, ymax = CI.upper),
                  alpha = 0.2, fill = "steelblue") +
      geom_line(color = "steelblue") +
      geom_point(size = 1.5, color = "steelblue") +
      labs(x = "Periods Relative to Treatment",
           y = "ATT (Incivility Rate)",
           title = paste0("Event Study (C&S): ", fig$name)) +
      theme_minimal(base_size = 12) +
      theme(plot.title = element_text(face = "bold"))

    save_figure(p_cs, paste0("fig_cs_eventstudy_", fig_key), width = 9, height = 5)
    message("  Saved: fig_cs_eventstudy_", fig_key)
  }

  rm(res_cs); gc()
}
```

## Per-figure coverage intensity maps

```{r coverage-maps}
if (!HAS_NP_STATES) {
  message("Skipping coverage maps — newspaper_states.csv not available.")
} else {
for (fig_key in names(FIGURES)) {
  fig <- FIGURES[[fig_key]]
  panel_path <- file.path(DATA_PANELS, paste0("did_panel_", fig_key, ".parquet"))

  if (!file.exists(panel_path)) {
    message("No panel for ", fig$name, ", skipping map.")
    next
  }

  message("Generating coverage map for: ", fig$name)

  panel <- as.data.table(read_parquet(panel_path))

  # Per-newspaper coverage info
  np_info <- panel[, .(
    ever_treated = max(as.integer(!is.na(treat_date)), na.rm = TRUE),
    total_figure_articles = sum(figure_count, na.rm = TRUE)
  ), by = newspaper_name]

  # Merge with state mapping
  np_info <- merge(np_info, np_states[, .(newspaper_name, state)],
                   by = "newspaper_name", all.x = TRUE)

  # Fuzzy match for unmatched: try both directions of startsWith
  # (panel name may be truncated OR may be the longer form)
  unmatched <- np_info[is.na(state)]
  if (nrow(unmatched) > 0) {
    n_fuzzy_matched <- 0L
    for (i in seq_len(nrow(unmatched))) {
      panel_nm <- unmatched$newspaper_name[i]
      # Skip very short names (< 5 chars) to avoid spurious matches
      if (nchar(panel_nm) < 5) next
      # Try: np_states name starts with panel name (panel is shorter)
      matches <- np_states[startsWith(newspaper_name, panel_nm)]
      if (nrow(matches) == 0) {
        # Try: panel name starts with np_states name (np_states has abbreviation)
        # Guard: require np_states name also >= 5 chars to avoid spurious matches
        matches <- np_states[nchar(newspaper_name) >= 5 &
                             mapply(startsWith, panel_nm, newspaper_name)]
      }
      if (nrow(matches) > 0) {
        np_info[newspaper_name == panel_nm, state := matches$state[1]]
        n_fuzzy_matched <- n_fuzzy_matched + 1L
      }
    }
    n_still_unmatched <- sum(is.na(np_info$state))
    message("  State mapping: ", nrow(np_info) - n_still_unmatched, " matched, ",
            n_fuzzy_matched, " via fuzzy, ", n_still_unmatched, " unmatched")
  }

  # State-level summary
  state_summary <- np_info[!is.na(state), .(
    n_treated = sum(ever_treated == 1),
    n_control = sum(ever_treated == 0),
    total_articles = sum(total_figure_articles[ever_treated == 1])
  ), by = state]

  state_summary[, intensity := fifelse(
    total_articles == 0, "None",
    fifelse(total_articles <= 25, "Low (1\u201325)",
    fifelse(total_articles <= 75, "Medium (26\u201375)",
            "High (76+)"))
  )]
  state_summary[, intensity := factor(intensity,
    levels = c("None", "Low (1\u201325)", "Medium (26\u201375)", "High (76+)")
  )]

  p_map <- plot_usmap(
    data = state_summary, values = "intensity",
    regions = "states", labels = FALSE
  ) +
    scale_fill_manual(
      values = c("None" = "grey90",
                 "Low (1\u201325)" = "#FFCDD2",
                 "Medium (26\u201375)" = "#E53935",
                 "High (76+)" = "#B71C1C"),
      na.value = "grey90",
      name = paste0(fig$name, "\nArticles")
    ) +
    labs(title = paste0("Coverage Intensity: ", fig$name),
         subtitle = paste0("Study window: ", fig$study_start, "\u2013", fig$study_end)) +
    theme(
      legend.position = "right",
      plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
      plot.subtitle = element_text(size = 10, hjust = 0.5, color = "gray30"),
      legend.text = element_text(size = 10),
      legend.title = element_text(size = 11)
    )

  save_figure(p_map, paste0("fig_coverage_map_", fig_key), width = 10, height = 6)
  message("  Saved: fig_coverage_map_", fig_key)

  rm(panel, np_info, state_summary); gc()
}
} # end if (HAS_NP_STATES)
```

## Per-figure incivility time series (treated vs control)

```{r timeseries-plots}
for (fig_key in names(FIGURES)) {
  fig <- FIGURES[[fig_key]]
  panel_path <- file.path(DATA_PANELS, paste0("did_panel_", fig_key, ".parquet"))

  if (!file.exists(panel_path)) {
    message("No panel for ", fig$name, ", skipping time series.")
    next
  }

  message("Generating time series for: ", fig$name)

  panel <- as.data.table(read_parquet(panel_path))
  panel[, ever_treated := as.integer(!is.na(treat_date))]

  # FIXED: For staggered DiD, the calendar-time plot with ever_treated grouping
  # is misleading because treated units are "pre-treatment" at different calendar times.
  # Instead, show:
  #   1. A relative-time plot centered on treatment onset (for treated units)
  #   2. Never-treated units shown as a baseline mean

  # Relative-time panel for treated units
  panel_treated <- panel[ever_treated == 1]
  if (nrow(panel_treated) > 0) {
    panel_treated[, rel_time := time_id - treat_time_id]

    # Average incivility by relative time
    rel_ts <- panel_treated[rel_time >= -24 & rel_time <= 24, .(
      mean_incivil = mean(incivil_rate_rf, na.rm = TRUE),
      n_obs = .N
    ), by = rel_time]
    setorder(rel_ts, rel_time)

    # Baseline: average incivility for never-treated units
    control_mean <- panel[ever_treated == 0, mean(incivil_rate_rf, na.rm = TRUE)]

    if (nrow(rel_ts) > 0) {
      p_ts <- ggplot(rel_ts, aes(x = rel_time, y = mean_incivil)) +
        geom_vline(xintercept = -0.5, linetype = "dotted", color = "gray40") +
        geom_line(color = "firebrick", linewidth = 0.8) +
        geom_point(color = "firebrick", size = 1.5)

      # Only add never-treated baseline if there are control units
      ts_subtitle <- "Treated newspapers centered on treatment date"
      if (!is.na(control_mean) && is.finite(control_mean)) {
        p_ts <- p_ts +
          geom_hline(yintercept = control_mean, linetype = "dashed",
                     color = "steelblue", linewidth = 0.8) +
          annotate("text", x = 20, y = control_mean,
                   label = "Never-treated mean", color = "steelblue",
                   vjust = -0.5, size = 3.5)
        ts_subtitle <- paste0(ts_subtitle, "; dashed = never-treated mean")
      }

      p_ts <- p_ts +
        labs(x = "Months Relative to Treatment Onset",
             y = "Mean Incivility Rate",
             title = paste0("Incivility Around Treatment Onset — ", fig$name),
             subtitle = ts_subtitle) +
        theme_minimal(base_size = 12) +
        theme(plot.title = element_text(face = "bold"))

      save_figure(p_ts, paste0("fig_timeseries_", fig_key), width = 9, height = 5)
      message("  Saved: fig_timeseries_", fig_key)
    }
  }

  rm(panel); gc()
}
```

## RF model figures (copy to Overleaf)

```{r rf-figures}
# These are generated in 05_random_forest.Rmd; just copy to Overleaf
for (fig_name in c("rf_variable_importance", "rf_calibration")) {
  for (ext in c("pdf", "png")) {
    src <- file.path(FIGURES_DIR, paste0(fig_name, ".", ext))
    if (file.exists(src)) {
      file.copy(src, file.path(OVERLEAF_FIGURES, paste0(fig_name, ".", ext)),
                overwrite = TRUE)
    }
  }
}
message("RF model figures copied to Overleaf.")
```

## Cross-figure ATT forest plot

```{r forest-plot}
if (length(forest_data) > 0) {
  forest_dt <- rbindlist(forest_data)
  forest_dt[, figure := factor(figure, levels = rev(figure))]

  # Dynamic height based on number of figures (0.5 inches per figure + 2 for margins)
  plot_height <- max(7, nrow(forest_dt) * 0.5 + 2)

  p_forest <- ggplot(forest_dt, aes(x = att, y = figure)) +
    geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
    geom_point(size = 3, color = "firebrick") +
    geom_errorbarh(aes(xmin = ci_lo, xmax = ci_hi), height = 0.25,
                   color = "firebrick") +
    labs(x = "ATT (IFE Estimator)",
         y = NULL,
         title = "ATT Comparison Across Political Figures",
         subtitle = "Interactive Fixed Effects estimator with 95% CI") +
    theme_minimal(base_size = 12) +
    theme(
      plot.title = element_text(face = "bold", size = 14),
      plot.subtitle = element_text(color = "gray40"),
      axis.text.y = element_text(size = 10)
    )

  save_figure(p_forest, "fig_forest_att_comparison", width = 10, height = plot_height)
  print(p_forest)
  message("Cross-figure forest plot saved.")
} else {
  message("No IFE models found — forest plot skipped.")
}
```

## Cross-figure summary table

```{r cross-figure-table}
if (length(forest_data) > 0) {
  summary_dt <- rbindlist(forest_data)

  # Add p-values
  summary_dt[, p_value := 2 * pnorm(-abs(att / se))]
  summary_dt[, `:=`(
    ATT     = sprintf("%.4f", att),
    SE      = sprintf("%.4f", se),
    CI      = paste0("[", sprintf("%.4f", ci_lo), ", ", sprintf("%.4f", ci_hi), "]"),
    p       = ifelse(p_value < 0.001, "$<$0.001", sprintf("%.3f", p_value))
  )]

  tex_lines <- c(
    "\\begin{table}[htbp]",
    "\\caption{IFE ATT Estimates Across All Political Figures\\label{tab:cross-figure}}",
    "\\centering",
    "\\begin{tabular}{lcccc}",
    "\\toprule",
    "Figure & ATT & SE & 95\\% CI & $p$-value \\\\",
    "\\midrule"
  )

  for (i in seq_len(nrow(summary_dt))) {
    tex_lines <- c(tex_lines,
      paste0(summary_dt$figure[i], " & ",
             summary_dt$ATT[i], " & ",
             summary_dt$SE[i], " & ",
             summary_dt$CI[i], " & ",
             summary_dt$p[i], " \\\\")
    )
  }

  tex_lines <- c(tex_lines,
    "\\bottomrule",
    "\\end{tabular}",
    "\\vspace{2pt}",
    "\\footnotesize\\textit{Note:} ATT estimated via Interactive Fixed Effects (IFE) ",
    "with bootstrap standard errors (200 replications).",
    "\\end{table}"
  )

  tex_string <- paste(tex_lines, collapse = "\n")
  save_table(tex_string, "table_cross_figure_ife")
  message("Cross-figure IFE summary table saved.")
  cat(tex_string, "\n")
} else {
  message("No IFE models found — cross-figure table skipped.")
}
```

## Aggregate incivility over time — national, regional, and state-level

```{r load-all-rf-scored}
# Load all RF-scored articles and compute yearly incivility by newspaper
rf_scored_dir <- file.path(DATA_PANELS, "rf_scored")
rf_files <- list.files(rf_scored_dir, pattern = "\\.parquet$", full.names = TRUE)

if (length(rf_files) > 0) {
  message("Loading ", length(rf_files), " RF-scored year files for aggregate plots...")

  yearly_np <- list()
  for (rf_f in rf_files) {
    yr <- gsub(".*rf_scored_(\\d{4})\\.parquet", "\\1", rf_f)
    dt_yr <- as.data.table(read_parquet(rf_f,
      col_select = c("newspaper_name", "year", "p_incivil")))
    # Aggregate to newspaper x year
    agg <- dt_yr[, .(
      mean_incivil = mean(p_incivil, na.rm = TRUE),
      n_articles = .N
    ), by = .(newspaper_name, year)]
    yearly_np[[yr]] <- agg
    rm(dt_yr, agg); gc()
  }

  np_year <- rbindlist(yearly_np)
  rm(yearly_np); gc()
  message("Aggregate data: ", nrow(np_year), " newspaper-year observations, ",
          uniqueN(np_year$newspaper_name), " newspapers, ",
          uniqueN(np_year$year), " years")

  # Merge with state mapping
  np_year <- merge(np_year, np_states[, .(newspaper_name, state)],
                   by = "newspaper_name", all.x = TRUE)

  # Fuzzy match for unmatched: try both directions of startsWith
  unmatched_agg <- np_year[is.na(state), unique(newspaper_name)]
  if (length(unmatched_agg) > 0) {
    for (panel_nm in unmatched_agg) {
      if (nchar(panel_nm) < 5) next
      matches <- np_states[startsWith(newspaper_name, panel_nm)]
      if (nrow(matches) == 0) {
        matches <- np_states[nchar(newspaper_name) >= 5 &
                             mapply(startsWith, panel_nm, newspaper_name)]
      }
      if (nrow(matches) > 0) {
        np_year[newspaper_name == panel_nm, state := matches$state[1]]
      }
    }
  }

  message("Newspapers with state match: ",
          uniqueN(np_year[!is.na(state), newspaper_name]), " / ",
          uniqueN(np_year$newspaper_name))

  # Define Census regions
  np_year[, region := fcase(
    state %in% c("CT","ME","MA","NH","RI","VT","NJ","NY","PA"), "Northeast",
    state %in% c("IL","IN","IA","KS","MI","MN","MO","NE","ND","OH","SD","WI"), "Midwest",
    state %in% c("AL","AR","DE","FL","GA","KY","LA","MD","MS","NC","OK","SC",
                 "TN","TX","VA","WV","DC"), "South",
    state %in% c("AZ","CO","ID","MT","NV","NM","OR","UT","WA","WY","CA","AK","HI"), "West",
    default = NA_character_
  )]
} else {
  message("No RF-scored files found — skipping aggregate incivility plots.")
  np_year <- NULL
}
```

### Figure: National incivility trend

```{r fig-national-incivility}
if (!is.null(np_year) && nrow(np_year) > 0) {
  # Weighted mean incivility per year (weighted by article count)
  national <- np_year[, .(
    mean_incivil = weighted.mean(mean_incivil, n_articles, na.rm = TRUE),
    n_newspapers = uniqueN(newspaper_name),
    n_articles = sum(n_articles)
  ), by = year]
  national <- national[is.finite(mean_incivil)]  # drop NaN from years with no valid data
  setorder(national, year)

  p_national <- ggplot(national, aes(x = year, y = mean_incivil)) +
    geom_line(color = "firebrick", linewidth = 0.8) +
    geom_smooth(method = "loess", span = 0.15, se = TRUE,
                color = "gray30", fill = "gray80", alpha = 0.3) +
    labs(x = "Year", y = "Mean Incivility (RF Score)",
         title = "Newspaper Incivility in the United States, 1774\u20131960",
         subtitle = "Article-weighted annual average across all newspapers") +
    theme_minimal(base_size = 12) +
    theme(
      plot.title = element_text(face = "bold", size = 14),
      plot.subtitle = element_text(color = "gray40")
    )

  save_figure(p_national, "fig_national_incivility_trend", width = 10, height = 6)
  print(p_national)
  message("National incivility trend saved.")
}
```

### Figure: Incivility by Census region over time

```{r fig-regional-incivility}
if (!is.null(np_year) && nrow(np_year[!is.na(region)]) > 0) {
  regional <- np_year[!is.na(region), .(
    mean_incivil = weighted.mean(mean_incivil, n_articles, na.rm = TRUE),
    n_newspapers = uniqueN(newspaper_name),
    n_articles = sum(n_articles)
  ), by = .(year, region)]
  setorder(regional, region, year)

  # Filter to regions with reasonable coverage (at least 3 newspapers in a year)
  regional <- regional[n_newspapers >= 3]

  p_region <- ggplot(regional, aes(x = year, y = mean_incivil, color = region)) +
    geom_line(alpha = 0.4, linewidth = 0.4) +
    geom_smooth(method = "loess", span = 0.2, se = FALSE, linewidth = 1) +
    scale_color_manual(values = c(
      "Northeast" = "#1b9e77",
      "Midwest"   = "#d95f02",
      "South"     = "#7570b3",
      "West"      = "#e7298a"
    )) +
    labs(x = "Year", y = "Mean Incivility (RF Score)",
         title = "Newspaper Incivility by U.S. Census Region",
         subtitle = "Smoothed trends; regions with \u22653 newspapers per year",
         color = "Region") +
    theme_minimal(base_size = 12) +
    theme(
      plot.title = element_text(face = "bold", size = 14),
      plot.subtitle = element_text(color = "gray40"),
      legend.position = "bottom"
    )

  save_figure(p_region, "fig_regional_incivility_trend", width = 10, height = 6)
  print(p_region)
  message("Regional incivility trend saved.")
}
```

### Figure: Incivility by state over time

```{r fig-state-incivility, fig.width=12, fig.height=10}
if (!is.null(np_year) && nrow(np_year[!is.na(state)]) > 0) {
  state_year <- np_year[!is.na(state), .(
    mean_incivil = weighted.mean(mean_incivil, n_articles, na.rm = TRUE),
    n_newspapers = uniqueN(newspaper_name),
    n_articles = sum(n_articles)
  ), by = .(year, state, region)]
  setorder(state_year, state, year)

  # Keep only states with at least 10 years of data and at least 2 newspapers on avg
  state_coverage <- state_year[, .(
    n_years = uniqueN(year),
    avg_np = mean(n_newspapers)
  ), by = state]
  keep_states <- state_coverage[n_years >= 10 & avg_np >= 2, state]
  state_plot <- state_year[state %in% keep_states]

  message("States with sufficient coverage: ", length(keep_states),
          " out of ", uniqueN(state_year$state))

  if (nrow(state_plot) > 0) {
    # region column already present from state_year aggregation (via np_year)

    p_state <- ggplot(state_plot, aes(x = year, y = mean_incivil,
                                       color = region, group = state)) +
      geom_line(alpha = 0.6, linewidth = 0.5) +
      facet_wrap(~ state, scales = "free_y", ncol = 6) +
      scale_color_manual(values = c(
        "Northeast" = "#1b9e77",
        "Midwest"   = "#d95f02",
        "South"     = "#7570b3",
        "West"      = "#e7298a",
        "Other"     = "gray50"
      )) +
      labs(x = "Year", y = "Incivility",
           title = "Newspaper Incivility by State",
           subtitle = "States with \u226510 years of data and \u22652 newspapers on average",
           color = "Region") +
      theme_minimal(base_size = 9) +
      theme(
        plot.title = element_text(face = "bold", size = 14),
        plot.subtitle = element_text(color = "gray40", size = 10),
        strip.text = element_text(face = "bold", size = 8),
        axis.text.x = element_text(angle = 45, hjust = 1, size = 6),
        axis.text.y = element_text(size = 6),
        legend.position = "bottom",
        panel.spacing = unit(0.3, "lines")
      )

    save_figure(p_state, "fig_state_incivility_trend", width = 14, height = 10)
    print(p_state)
    message("State-level incivility trend saved.")
  }
}
```

## Export: newspaper-level incivility summary CSV

```{r newspaper-csv}
if (!is.null(np_year) && nrow(np_year) > 0) {
  newspaper_summary <- np_year[, .(
    state          = state[1],
    region         = region[1],
    first_year     = min(year),
    last_year      = max(year),
    n_years        = uniqueN(year),
    total_articles = sum(n_articles),
    mean_incivil   = round(weighted.mean(mean_incivil, n_articles, na.rm = TRUE), 6),
    # Weighted SD of yearly means (between-year variation, article-weighted)
    sd_incivil     = round({
      wm <- weighted.mean(mean_incivil, n_articles, na.rm = TRUE)
      sqrt(sum(n_articles * (mean_incivil - wm)^2, na.rm = TRUE) /
           max(1, sum(n_articles) - 1))
    }, 6),
    min_incivil    = round(min(mean_incivil, na.rm = TRUE), 6),
    max_incivil    = round(max(mean_incivil, na.rm = TRUE), 6)
  ), by = newspaper_name]

  setorder(newspaper_summary, -mean_incivil)

  csv_path <- file.path(DATA_PANELS, "newspaper_incivility_summary.csv")
  write.csv(newspaper_summary, csv_path, row.names = FALSE)
  message("Saved newspaper summary: ", csv_path,
          " (", nrow(newspaper_summary), " newspapers)")

  # Quick stats
  message("  Mean incivility across newspapers: ",
          round(mean(newspaper_summary$mean_incivil, na.rm = TRUE), 4))
  message("  Most incivil: ", newspaper_summary$newspaper_name[1],
          " (", newspaper_summary$mean_incivil[1], ")")
  message("  Least incivil: ", newspaper_summary$newspaper_name[nrow(newspaper_summary)],
          " (", newspaper_summary$mean_incivil[nrow(newspaper_summary)], ")")
}
```

## Final file listing

```{r file-listing}
message("\n=== Files in Overleaf Figures ===")
cat(paste(list.files(OVERLEAF_FIGURES), collapse = "\n"), "\n")

message("\n=== Files in Overleaf Tables ===")
cat(paste(list.files(OVERLEAF_TABLES), collapse = "\n"), "\n")

message("\n=== Files in local figures/ ===")
cat(paste(list.files(FIGURES_DIR), collapse = "\n"), "\n")

message("\n=== Files in local tables/ ===")
cat(paste(list.files(TABLES_DIR), collapse = "\n"), "\n")

message("\nAll figures and tables exported successfully.")
```
